Here are a collection of my S\+DX mods that are available to all to re-\/use and re-\/integrate as you see fit.

Mods are available to be downloaded here\+: \mbox{[}url\mbox{]}\href{https://github.com/7D2DMods/SDXMods}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods}}\mbox{[}/url\mbox{]}

The Sphere\+II P\+G13 mod is available here\+: \mbox{[}url\mbox{]}\href{https://github.com/7D2DMods/Mods/tree/master/SphereII_PG13}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+Mods/tree/master/\+Sphere\+I\+I\+\_\+\+P\+G13}}\mbox{[}/url\mbox{]}

\mbox{[}table=class\+: grid, align\+: center\mbox{]} \mbox{[}tr\mbox{]} \mbox{[}th\mbox{]}Mod Name\mbox{[}/th\mbox{]} \mbox{[}th\mbox{]}More Info\mbox{[}/th\mbox{]} \mbox{[}th\mbox{]}Description\mbox{[}/th\mbox{]} \mbox{[}th\mbox{]}Type\mbox{[}/th\mbox{]} \mbox{[}/tr\mbox{]} \mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}Sphere\+I\+I\+\_\+\+P\+G13\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/Mods/tree/master/SphereII_PG13}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+Mods/tree/master/\+Sphere\+I\+I\+\_\+\+P\+G13}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}This mod swaps the Stripper mesh with that of the Nurses\textquotesingle{}, for those players who do not want to see the strippers.

It also updates the trader that Dislikes you, and makes him more Neutral.\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}Vanilla Modlet\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]} \mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}Animation\+S\+DX\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}Allows animations and custom entities\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]}

\mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}Zombie Transmogrifier\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}Randomzies Zombie walk types\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]}

\mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}Sphere\+II Entity Player\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}Allows a player class to be over-\/ridden, giving some new features, such as one-\/block crouch\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]} \mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}Sphere\+II Mod Localization\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}Gap solution to allow localization to be read from the Mods folder, and merged into the main localization file, in-\/memory.\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]} \mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}Sphere\+II Unlock Enemy Health Bar\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}Gap solution to allow you to unlock the enemy health bar, for better or for worse.\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]} \mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}Sphere\+II and Xyth\textquotesingle{}s Music and Video Player\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}Introduce Music and Video Players, as well as C\+Ds and D\+V\+Ds into your S\+DX world.\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]} \mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}Sphere\+II Take And Replace\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}This mod, as configured by default, will allow the player to take the boards off of boarded up windows. Players will be able to peel off the boards on windows and storage crate boxes that typically need to be axed down, based on a timer. This timer is set by default to be 15 seconds, and is configurable through X\+ML.\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]} \mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}SyX Security Bots\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}In the fight against the degredation of society, SyX Security has produced a series of counter-\/measures against the so-\/called \char`\"{}zombie apocalypse\char`\"{}. Deployed in infected hotspots around the world, these counter-\/measures have been designed to reduce and ultimately send the zombie apocalypse into remission.

Warning\+: These hot spots are extremely dangerous for the non-\/infected, and any survivors are strongly recommended to be evacuated before they are deployed.\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]} \mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}Sphere\+II Wandering Traders\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}This mod allows traders to wander and roam about the world, selling their wares and fighting the zombies. Requires \mbox{[}U\+RL=\href{https://github.com/7D2D/A17SDXMods/tree/master/Xyth_WanderingTraders}{\texttt{ https\+://github.\+com/7\+D2\+D/\+A17\+S\+D\+X\+Mods/tree/master/\+Xyth\+\_\+\+Wandering\+Traders}}\mbox{]}Xyth\textquotesingle{}s Wandering Traders\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]}

\mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://7daystodie.com/forums/showthread.php?103783-sphereii-s-SDX-Mods&p=970064&viewfull=1\#post970064}{\texttt{ https\+://7daystodie.\+com/forums/showthread.\+php?103783-\/sphereii-\/s-\/\+S\+D\+X-\/\+Mods\&p=970064\&viewfull=1\#post970064}}\mbox{]}Clear UI\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}Based on the original \mbox{[}U\+RL=\href{https://7daystodie.com/forums/showthread.php?68042-DadMod}{\texttt{ https\+://7daystodie.\+com/forums/showthread.\+php?68042-\/\+Dad\+Mod}}\mbox{]}D\+AD mod\mbox{[}/\+U\+RL\mbox{]}, this mod removes all main UI elements\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]}

\mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://7daystodie.com/forums/showthread.php?103783-sphereii-s-SDX-Mods&p=970059&viewfull=1\#post970059}{\texttt{ https\+://7daystodie.\+com/forums/showthread.\+php?103783-\/sphereii-\/s-\/\+S\+D\+X-\/\+Mods\&p=970059\&viewfull=1\#post970059}}\mbox{]}Anti\+Nerd\+Pole\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}Disables placing of blocks when you are not on the ground, but allows placing if on ladder.\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]} \mbox{[}/table\mbox{]}

The follow S\+DX Mods are more of \char`\"{}\+Core\char`\"{} mods that add new abilities and features for modders to use. It\textquotesingle{}s recommended that they be used together. A large amount of code and features were added to these to allow modders flexibility.

These are community mods\+: You may contribute code and fixes, and freely re-\/use them.

\mbox{[}i\mbox{]}These do not represent a complete play through or experience. They are meant to be consumed by modders into their mods and balanced.\mbox{[}/i\mbox{]}

Combined, they can be used to create a more realistic world with N\+P\+Cs, allowing you to hire each entity using different currencies. You can also be rewarded N\+P\+Cs based on certain quest chains. Some N\+P\+Cs can even follow you if you are holding a special block or item in your hand.

Once hired, you can ask the N\+PC to perform various duties, such as following you, helping you loot a poi, patrol a section of your base, or just stay still.

Don\textquotesingle{}t think you can allow yourself unlimited N\+P\+Cs. These N\+P\+Cs have a Maslow AI task, which makes them hungry and thirsty. Be sure to have food and drink nearby so they can drink and eat when they need it.

A small extension to the \mbox{\hyperlink{class_entity_alive_s_d_x}{Entity\+Alive\+S\+DX}} is the Farming animal mod, Bloom\textquotesingle{}s Family Animal Husbandry. Find and tame animals herds, or get rewarded through quests lines. Same rules apply as the N\+P\+Cs, you need to make sure you have food and water near by. Same Cows, sheep, chickens and pigs are packaged inside of them.

N\+P\+Cs and Animals\textquotesingle{}s life cycles can be control through buff sequences, allowing the animals to grow from babies to seniors, eventually dying of old age.

A tremendous amount of thanks to Xyth and Khaine for their tireless testing, entity creation and feature ideas.

\mbox{[}table=class\+: grid, align\+: center\mbox{]} \mbox{[}tr\mbox{]} \mbox{[}th\mbox{]}Mod Name\mbox{[}/th\mbox{]} \mbox{[}th\mbox{]}More Info\mbox{[}/th\mbox{]} \mbox{[}th\mbox{]}Description\mbox{[}/th\mbox{]} \mbox{[}th\mbox{]}Type\mbox{[}/th\mbox{]} \mbox{[}/tr\mbox{]} \mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://7daystodie.com/forums/showthread.php?103783-sphereii-s-SDX-Mods&p=969913&viewfull=1\#post969913}{\texttt{ https\+://7daystodie.\+com/forums/showthread.\+php?103783-\/sphereii-\/s-\/\+S\+D\+X-\/\+Mods\&p=969913\&viewfull=1\#post969913}}\mbox{]}S\+D\+X\+\_\+\+Buffs\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods/tree/master/SDX_Buffs}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods/tree/master/\+S\+D\+X\+\_\+\+Buffs}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]}

\mbox{[}td\mbox{]}This S\+DX Mod adds additional Action events and Requirements that can be used in the buffs.\+xml.\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]} \mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://7daystodie.com/forums/showthread.php?103783-sphereii-s-SDX-Mods&p=969915&viewfull=1\#post969915}{\texttt{ https\+://7daystodie.\+com/forums/showthread.\+php?103783-\/sphereii-\/s-\/\+S\+D\+X-\/\+Mods\&p=969915\&viewfull=1\#post969915}}\mbox{]}S\+D\+X\+\_\+\+Quests\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods/tree/master/SDX_Quests}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods/tree/master/\+S\+D\+X\+\_\+\+Quests}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}The follow classes have been added to allow more fine tuning of the Quest system, by introducing new Objectives and action types.\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://7daystodie.com/forums/showthread.php?103783-sphereii-s-SDX-Mods&p=969918&viewfull=1\#post969918}{\texttt{ https\+://7daystodie.\+com/forums/showthread.\+php?103783-\/sphereii-\/s-\/\+S\+D\+X-\/\+Mods\&p=969918\&viewfull=1\#post969918}}\mbox{]}\mbox{\hyperlink{class_s_d_x_dialog}{S\+D\+X\+Dialog}}\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods/tree/master/SDX_Dialog}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods/tree/master/\+S\+D\+X\+\_\+\+Dialog}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}The S\+DX Dialog adds in new actions and triggers used for the dialogs.\+xml, as well as include new UI controllers. \mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]}

\mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://7daystodie.com/forums/showthread.php?103783-sphereii-s-SDX-Mods&p=969919&viewfull=1\#post969919}{\texttt{ https\+://7daystodie.\+com/forums/showthread.\+php?103783-\/sphereii-\/s-\/\+S\+D\+X-\/\+Mods\&p=969919\&viewfull=1\#post969919}}\mbox{]}\mbox{\hyperlink{class_entity_alive_s_d_x}{Entity\+Alive\+S\+DX}}\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods/tree/master/SDX_EntityAliveSDX}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods/tree/master/\+S\+D\+X\+\_\+\+Entity\+Alive\+S\+DX}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}This project contains a few different classes to enable more flexible N\+P\+Cs and animals.\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]}

\mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://7daystodie.com/forums/showthread.php?103783-sphereii-s-SDX-Mods&p=969921&viewfull=1\#post969921}{\texttt{ https\+://7daystodie.\+com/forums/showthread.\+php?103783-\/sphereii-\/s-\/\+S\+D\+X-\/\+Mods\&p=969921\&viewfull=1\#post969921}}\mbox{]}E\+AI Tasks\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods/tree/master/SDX_EAITasks}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods/tree/master/\+S\+D\+X\+\_\+\+E\+A\+I\+Tasks}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}The S\+D\+X\+\_\+\+E\+A\+I\+Tasks class introduces new AI tasks for entities to perform. Some of the tasks were changed so they rely on entity factions, rather than specifying the enemies through their Entity classes.\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]}

\mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://7daystodie.com/forums/showthread.php?103783-sphereii-s-SDX-Mods&p=969923&viewfull=1\#post969923}{\texttt{ https\+://7daystodie.\+com/forums/showthread.\+php?103783-\/sphereii-\/s-\/\+S\+D\+X-\/\+Mods\&p=969923\&viewfull=1\#post969923}}\mbox{]}Spawn From Entity\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods/tree/master/SDX_SpawnFromEntityGroup}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods/tree/master/\+S\+D\+X\+\_\+\+Spawn\+From\+Entity\+Group}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}This class attempts to provide an entity spawning mechanism based on an entity. Rather than using the block spawner, this entity will spawn in a specified group of entities, assign a leader to them. It\textquotesingle{}s designed to be a Herd or Bandit / N\+PC group spawner\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]}

\mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://7daystodie.com/forums/showthread.php?103783-sphereii-s-SDX-Mods&p=969924&viewfull=1\#post969924}{\texttt{ https\+://7daystodie.\+com/forums/showthread.\+php?103783-\/sphereii-\/s-\/\+S\+D\+X-\/\+Mods\&p=969924\&viewfull=1\#post969924}}\mbox{]}Bloom\textquotesingle{}s Animal Husbandry\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods/tree/master/Blooms_AnimalHusbandry}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods/tree/master/\+Blooms\+\_\+\+Animal\+Husbandry}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}The Bloom\textquotesingle{}s Animal Husbandry Mod provides sample xml for a cow, along with support X\+ML items, such as hand item, buff sequences to control its thirst and hunger, as well as reproduction. \mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]}

\mbox{[}tr\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://7daystodie.com/forums/showthread.php?103783-sphereii-s-SDX-Mods&p=969926&viewfull=1\#post969926}{\texttt{ https\+://7daystodie.\+com/forums/showthread.\+php?103783-\/sphereii-\/s-\/\+S\+D\+X-\/\+Mods\&p=969926\&viewfull=1\#post969926}}\mbox{]}a\+X\+Ui\+\_\+\+Dialog\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}\mbox{[}U\+RL=\href{https://github.com/7D2DMods/SDXMods/tree/master/aXUi_Dialog}{\texttt{ https\+://github.\+com/7\+D2\+D\+Mods/\+S\+D\+X\+Mods/tree/master/a\+X\+Ui\+\_\+\+Dialog}}\mbox{]}Info\mbox{[}/\+U\+RL\mbox{]}\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}The a\+X\+Ui\+\_\+\+Dialog provides a sample X\+UI from Sirillion to allow the N\+P\+Cs to have a different dialog display format, including a sample N\+PC dialog with a quest chain.

\mbox{[}/td\mbox{]} \mbox{[}td\mbox{]}S\+DX\mbox{[}/td\mbox{]} \mbox{[}/tr\mbox{]}

\mbox{[}/table\mbox{]} 